\chapter{User Manual}

\section{Introduction}

\subsection{Purpose}

The purpose of the system is to easily manage the stock of the products sold at a Veterinary Center. The system achieves this purpose with the following features:

\begin{itemize}
\item{Automatically updating the stock of the products when they are purchased by a customer}
\item{Informing the user when stock needs to be moved from one location to another}
\item{informing the user that they need to buy more stock for specific products when the total stock is low.}
\end{itemize}

\subsection{Intended Audience}

The intended audience for my system is Beacon Veterinary Center. However, with minor changes to the system, such as the logo and the information stored about the product, the system could potentially be used by any company that sells products. 

\section{Installation}

\subsection{Prerequisite Installation}

%include as many subsubsections as necessary for each piece of required software

\subsubsection{Installing Python}

\subsubsection{Installing PyQt}

\subsubsection{Etc.}

\subsection{System Installation}

\subsection{Running the System}



\section{Tutorial}

\subsection{Introduction}
The following section explains how to use each component of the system. Each subsection of the tutorial gives a detailed explanation including annotated diagrams to assist you in running the system.


\subsection{Assumptions}

The Tutorial has been created under the assumption that the users will have a variety of different computer knowledge. Therefore, the tutorial has been created such that, minimal computer knowledge is required to understand it. Another assumption made, is that the system has been installed successfully, and that the system is already running. The installation tutorial can be found on page: section: and the tutorial on running the system can be found on page: section: 

\subsection{Tutorial Questions}
The following sections are a step by step guide for each section of the system. The different sections of the tutorial have been broken down into Questions which can be referenced in the contents table below:

\pagebreak
\subsubsection{Contents}

\begin{center}
    \begin{longtable}{|p{3cm}|p{6cm}|p{3cm}|}
        \hline
	 \textbf{Section Number} & \textbf{Question} & \textbf{Page Number} \\ \hline
	&How do I log in to the system? & \\ \hline
	&What should i do if i forget my user-name or password?& \\ \hline
	& What should i do if i can no longer access the email address associated with my account? & \\ \hline
	&How do i add a product to the system? & \\ \hline
	&How do i edit a product that is currently in the system?& \\ \hline
	&How do i remove a product from the system?& \\ \hline
	&How do i find a Product in the system?& \\ \hline
	&How do i change the stock of a product?& \\ \hline
	&How do i view the predicted sales of a product?& \\ \hline
	&How do i add a Member to the system?& \\ \hline
	&How do i find a Member in the system?& \\ \hline
	&How do i edit the information about a Member?& \\ \hline
	&How do i remove a Member from the system?& \\ \hline
	&How do i add an Employee to the system?& \\ \hline
	&How do i edit the information about an Employee in the system?& \\ \hline
	&How do i remove an employee from the system?& \\ \hline
	&How do i find an Employee in the system?& \\ \hline
	&How do i get to the Order interface?& \\ \hline
	&How do i add products to an order?& \\ \hline
	&How to i preview an order once its finished?& \\ \hline
	&How do i print off an invoice?& \\ \hline
	&How do send an invoice to an email?& \\ \hline
	&How do i change the company information on the invoice? & \\ \hline
	&How do i change the company logo on the invoice?& \\ \hline
	&Why won't emails send successfully?& \\ \hline
	&How do i change my password?& \\ \hline
	&How do i access the search window?& \\ \hline
	&How do i log off the system?& \\ \hline
	\end{longtable}
\end{center}

\subsubsection{Logging into the system}

\subsubsection{Logging off the system.}

\subsubsection{Forgetting Your User-name or Password}

\subsubsection{Unable to access your email address}

\subsubsection{Adding a Product to the system}

\subsubsection{Adding a Member to the system}

\subsubsection{Adding an Employee to the system}

\subsubsection{Editing a Product in the system}

\subsubsection{Editing a Member currently in the system}

\subsubsection{Editing an Employee in the system}

\subsubsection{Removing a Product from the system}

\subsubsection{Removing a Member from the system}

\subsubsection{Removing an Employee for the system.}

\subsubsection{Finding a Product within the system}

\subsubsection{Finding a Member in the system}

\subsubsection{Finding an Employee in the system}

\subsubsection{Changing the stock of a Product}

\subsubsection{Product Stock Prediction}

\subsubsection{Adding an Employee to the system}

\subsubsection{Creating an Order}

\subsubsection{Adding products to an order}

\subsubsection{Previewing the invoice}

\subsubsection{Printing an invoice}

\subsubsection{Emailing an invoice}

\subsubsection{Changing information on the invoice}

\subsubsection{Problems with sending emails}

\subsubsection{Changing your Password}

\subsubsection{Accessing the search window}




\subsection{Saving}

\subsection{Limitations}

\section{Error Recovery}

%include as many subsections as necessary for each error
\subsection{Error 1}

\subsection{Error 2}

\section{System Recovery}

\subsection{Backing-up Data}

\subsection{Restoring Data}