\chapter{Analysis}

\section{Introduction}

\subsection{Client Identification}

	\begin{flushleft}

My client is Tom Henderson; he is thirty seven years old and is the principle veterinary surgeon and managing director of Beacon Veterinary. Tom graduated from Melbourne University, Victoria, Australia in 2000 and found employment with the Beacon Vet Centre in Aspatria in 2003. Since then Tom has brought partnership in the practice. \par


	\end{flushleft}

\subsection{Define the current system}


Despite being a veterinary centre, Beacon vets sold roughly a dozen products, such as Vetericyn, a non toxic cut / wound treatment for animals. Because only a dozen items were being sold and only 1-3 products were sold at once, keeping track of the stock of each item was an extremely easy process./par

Last year Beacon Vets expanded on the range of the products they sold, providing a wide variety of foods and treatments for all sorts of animals such as dogs, cats and rabbits etc. Although Beacon Vets, greatly expanded on the products they sold, they did not change their system of keeping track of stock. The current system is a Microsoft Excel spreadsheet containing the information of the product, the selling price, the current amount in the front of store, the current amount being stored in the back of the store. This current system was useful and easy to use when handling a dozen products but has become difficult and confusing now many more products are being sold. here is the current Edexel Spreadsheet in use:\par

Every time products are sold, the document is manually changed.For example if the veternary sold 1 bag of dietry dog food, the Front of house stock would go from 7 to 6. When the stock in the front of house gets low, products are moved from the back of house to the front of house for the customers to buy. when the total stock gets low, an order of that specific product is made.\par

\subsection{Describe the problems}

There are many problems with the current system. Having to keep manually changing the document every time a product is sold, moved to the front of house or if a delivery comes in. Editing the document becomes tedious and sometimes errors are made changing the values. Selling the product and changing the document are two different processes. This is a problem as both these processes can be combined into one to improve the system./par

The current operating system on the computer is Windows 7. The program Microsoft Excel which may not be compatable with other operating systems such as Mac or Linux. This is a problem with the current system because if a new Computer is brought with a different operating system, the current system may not be compatable and usable on the new computer. If the current system is used for a long period of time (for example 5 years), The version of Excel the system was created in may not be compatible with an up to date version of Excel. This could also be problematic because it would mean the current system would stop functioning. A similar problem would be that the current system was created using an upto date version of Excel and the current version of Excel on the computer is not upto date, which could result in the System not being compatible with the version of Excel installed on the computer./par




\subsection{Section appendix}

\section{Investigation}


\subsection{The current system}

\subsubsection{Data sources and destinations}

\subsubsection{Algorithms}

\subsubsection{Data flow diagram}

\subsubsection{Input Forms, Output Forms, Report Formats}

\subsection{The proposed system}

\subsubsection{Data sources and destinations}

\subsubsection{Data flow diagram}

\subsubsection{Data dictionary}

\subsubsection{Volumetrics}

\section{Objectives}

\subsection{General Objectives}

\subsection{Specific Objectives}

\subsection{Core Objectives}

\subsection{Other Objectives}

\section{ER Diagrams and Descriptions}

\subsection{ER Diagram}

\subsection{Entity Descriptions}

\section{Object Analysis}

\subsection{Object Listing}

\subsection{Relationship diagrams}

\subsection{Class definitions}

\section{Other Abstractions and Graphs}

\section{Constraints}

\subsection{Hardware}

\subsection{Software}

\subsection{Time}

\subsection{User Knowledge}

\subsection{Access restrictions}

\section{Limitations}

\subsection{Areas which will not be included in computerisation}

\subsection{Areas considered for future computerisation}

\section{Solutions}

\subsection{Alternative solutions}

\subsection{Justification of chosen solution}
